### 2014-02-12 classicthesis/Chapters/Background.tex
acknowledgement geschreven en dedication aangepast
introductie begint beter te lopen

%************************************************
\chapter{Introduction to Learning-to-Rank}
Different definitions of Learning-to-Rank exist. In general, all methods that use machine learning technologies to solve the problem of ranking are called Learning-to-Rank methods.\\
Liu \cite{Liu2007} proposes a more narrow definition and only considers ranking methods to be a Learning-to-Rank method when it meets the following two properties:
\begin{description}
\item[Feature Based]{\emph{Feature based} means that all documents under investigation are represented by feature vectors that reflect the relevance of the documents to the query.}
\item[Discriminative Training]{\emph{Discriminative training} means that the learning process can be well described by the four components of discriminative learning, that is, a Learning-to-Rank method has its own input space, output space, hypothesis space, and loss function. Input space, output space, hypothesis space, and loss function are hereby defined as follows:
	\begin{description}
	\item[Input Space]{contains the objects under investigation. Usually objects are represented by feature vectors, extracted according to different applications.}
	\item[Output Space]{contains the learning target with respect to the input objects.}
	\item[Hypothesis Space]{defines the class of functions mapping the input space to the output space. The functions operate on the feature vectors of the input object, and make predictions according to the format of the output space.}
	\item[Loss Function]{In order to learn the optimal hypothesis, a training set is usually used, which contains a number of objects and their ground truth labels, sampled from the product of the input and output spaces.}
	\end{description}
\begin{figure}
\includegraphics[scale=0.4]{gfx/descriminative_training}
\caption{Machine learning framework for Learning-to-Rank, from Liu\cite{Liu2007}}
\label{fig:discriminative_training}
\end{figure}
Figure \ref{fig:discriminative_training} shows the relationships between input space, output space, hypothesis space and loss function.
}

Figure \ref{ref:ltr_framework} shows how the learning process in Learning-to-Rank typically happens. A set of queries $q_i$ with $n > i > 1$, the documents associated with these queries which are represented by feature vector $x_i$, and the relevant judgments of those documents $y_i$ are inputted to a learning algorithm that learns a ranking model such that the output of the ranking model can predict relevant judgment labels in this training set as accurately as possible. Later on we can test the accuracy of this ranking model by predicting the relevant judgments new documents given a new query.
\begin{figure}
\includegraphics[scale=0.3]{gfx/ltr_framework}
\caption{The Learning-to-Rank framework, from Liu\cite{Liu2007}}
\label{ref:ltr_framework}
\end{figure}

\end{description}
\chapter{Benchmark Datasets}
\chapter{Pointwise Approach}
\chapter{Pairwise Approach}
\chapter{Listwise Approach}
\chapter{Summary}

>>>>

%************************************************
\chapter{Introduction to Learning-to-Rank}
Different definitions of Learning-to-Rank exist. In general, all methods that use machine learning technologies to solve the problem of ranking are called Learning-to-Rank methods.\\
Liu \cite{Liu2007} proposes a more narrow definition and only considers ranking methods to be a Learning-to-Rank method when it meets the following two properties:
\begin{description}
\item[Feature Based]{\emph{Feature based} means that all documents under investigation are represented by feature vectors that reflect the relevance of the documents to the query.}
\item[Discriminative Training]{\emph{Discriminative training} means that the learning process can be well described by the four components of discriminative learning, that is, a Learning-to-Rank method has its own input space, output space, hypothesis space, and loss function. Input space, output space, hypothesis space, and loss function are hereby defined as follows:
	\begin{description}
	\item[Input Space]{contains the objects under investigation. Usually objects are represented by feature vectors, extracted according to different applications.}
	\item[Output Space]{contains the learning target with respect to the input objects.}
	\item[Hypothesis Space]{defines the class of functions mapping the input space to the output space. The functions operate on the feature vectors of the input object, and make predictions according to the format of the output space.}
	\item[Loss Function]{In order to learn the optimal hypothesis, a training set is usually used, which contains a number of objects and their ground truth labels, sampled from the product of the input and output spaces.}
	\end{description}
	}
\end{description}
\begin{figure}[!h]
\includegraphics[scale=0.26]{gfx/descriminative_training}
\caption{Machine learning framework for Learning-to-Rank, from Liu\cite{Liu2007}}
\label{fig:discriminative_training}
\end{figure}
Figure \ref{fig:discriminative_training} shows the relationships between input space, output space, hypothesis space and loss function.

Figure \ref{ref:ltr_framework} shows how the learning process in Learning-to-Rank typically happens. A set of queries $q_i$ with $n > i > 1$, the documents associated with these queries which are represented by feature vector $x_i$, and the relevant judgments of those documents $y_i$ are inputted to a learning algorithm that learns a ranking model such that the output of the ranking model can predict relevant judgment labels in this training set as accurately as possible. Later on we can test the accuracy of this ranking model by predicting the relevant judgments new documents given a new query.
\begin{figure}[!h]
\includegraphics[scale=0.25]{gfx/ltr_framework}
\caption{A typical Learning-to-Rank setting, from Liu\cite{Liu2007}}
\label{ref:ltr_framework}
\end{figure}\\

Learning-to-Rank algorithms can be classified into three approaches: the pointwise approach, the pairwise approach and the listwise approach, on which we will elaborate in the subsequent chapters.

\chapter{Benchmark Datasets}
\chapter{Pointwise Approach}
\chapter{Pairwise Approach}
\chapter{Listwise Approach}
\chapter{Summary}

### 2014-02-12 classicthesis/Chapters/Introduction.tex
introductie begint beter te lopen

%********************************************************************
% Appendix
%*******************************************************
% If problems with the headers: get headings in appendix etc. right
%\markboth{\spacedlowsmallcaps{Appendix}}{\spacedlowsmallcaps{Appendix}}
\chapter{Motivation and Problem Statement}
Several Learning to Rank (LTR) benchmark datasets have been proposed in recent years \cite{Chapelle2011a,Qin2010,Alcantara2010} (Yandex Internet Mathematics competition). Chapelle et al \cite{Chapelle2011b} observed that the top competitors' results in LTR competitions are very close to each other, which raises the presumption that high accuracy LTR is a 'solved problem'.\\

Chappelle et al \cite{Chapelle2011b} identified efficiency and scalability of LTR algorithms to be one of the most important directions of future research in the field of LTR. The rationale behind this observation is that IR datasets are becoming bigger and bigger and that algorithm efficiency and scalability has not played a role in any LTR benchmark so far.\\

Several attempts on parallel or distributed machine learning \cite{Chu2007,Chang2007} has been made. The work on parallel or distributed LTR is still very limited compared to the amount of work that has been done on parallel or distributed regular machine learning. The field of efficient LTR has been getting some attention lately \cite{Asadi2013a,Asadi2013b,Busa-Fekete2012,Sousa2012,Shukla2012} since Chapelle at all \cite{Chapelle2011b} stated its growing importance back in 2011, only few of these studies \cite{Sousa2012,Shukla2012} have explored the possibilities of efficient LTR through the use of parallel programming paradigms. Lin \cite{Lin2013} observed that algorithms that are of iterative nature, like most LTR algorithms, are not amenable to the MapReduce framework. Lin \cite{Lin2013} argued that iterative algorithms can often be replaced with non-iterative alternatives or can still be optimized in such a way that its performance in a MapReduce setting is good enough.\\

>>>>

%********************************************************************
% Appendix
%*******************************************************
% If problems with the headers: get headings in appendix etc. right
%\markboth{\spacedlowsmallcaps{Appendix}}{\spacedlowsmallcaps{Appendix}}
\chapter{Motivation and Problem Statement}
Ranking is a core problem in the field of information retrieval. The ranking task in information retrieval entails the ranking of candidate documents according to their relevance to a query. Heuristic ranking models have long been around in the information retrieval field. The increasing amounts of potential training data have recently made it possible to leverage machine learning methods to obtain more effective models. Learning-to-Rank is the relatively new research area covering the use of machine learning models for the ranking task.\\

In recent years several Learning-to-Rank benchmark datasets have been proposed that allow us to compare the performance of different Learning-to-Rank methods. Well-known benchmark datasets include the \emph{Yahoo! Learning to Rank Challenge} dataset\cite{Chapelle2011a}, the Yandex Internet Mathematics competition\footnote{http://imat-relpred.yandex.ru/en/}, and the LETOR dataset\cite{Qin2010} that was build by Microsoft Research. One of the concluding observations of the \emph{Yahoo! Learning to Rank Challenge} was that almost all work in the Learning-to-Rank field focuses on ranking accuracy and that efficiency and scalability of Learning-to-Rank algorithms is still an underexposed research area of which its importance is likely to increase in the near future as training sets are becoming larger and larger\cite{Chapelle2011b}. Liu\cite{Liu2007} confirms the observation that efficiency and scalability of Learning-to-Rank methods has so far been an overlooked research area in his influential book on Learning-to-Rank.\\

Some research has been done in the area of on parallel or distributed machine learning \cite{Chu2007,Chang2007}. However, almost none of these studies include the Learning-to-Rank subfield of machine learning. The field of efficient LTR has been getting some attention lately \cite{Asadi2013a,Asadi2013b,Busa-Fekete2012,Sousa2012,Shukla2012} since Chapelle at all \cite{Chapelle2011b} stated its growing importance back in 2011, only few of these studies \cite{Sousa2012,Shukla2012} have explored the possibilities of efficient LTR through the use of parallel programming paradigms. Lin \cite{Lin2013} observed that algorithms that are of iterative nature, like most LTR algorithms, are not amenable to the MapReduce framework. Lin \cite{Lin2013} argued that iterative algorithms can often be replaced with non-iterative alternatives or can still be optimized in such a way that its performance in a MapReduce setting is good enough.\\
